\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{John Doe}} \\[0.5em]
    123 Main Street \\ 
    Anytown, CA 12345 \\ 
    (123) 456-7890 \\ 
    johndoe@email.com \\ 
    \href{https://linkedin.com/in/johndoe}{linkedin.com/in/johndoe}
\end{center}

\vspace{1em}

\section*{Summary}
Dedicated and results-oriented \textbf{Data Scientist} with \textbf{5} years of experience in machine learning and data analysis. Proven ability to develop data-driven solutions that improve operational efficiency and enhance decision-making. Seeking to leverage expertise in big data technologies and statistical modeling to climate modeling and weather extreme events.

\section*{Education}
\textbf{Master of Science} \\
Data Science \\
University of California, Anytown, CA \\
September 2017 - June 2019 \\
\begin{itemize}[left=0pt]
    \item Relevant Coursework: Machine Learning, Statistical Methods, Data Visualization
    \item Honors: Dean's List, Graduated with Distinction
\end{itemize}

\section*{Experience}
\textbf{Data Scientist} \\
Tech Solutions Inc., Anytown, CA \\
July 2019 - Present \\
\begin{itemize}[left=0pt]
    \item Developed predictive models using Python and R, increasing sales forecasting accuracy by 25\%.
    \item Collaborated with cross-functional teams to analyze customer behavior and optimize marketing strategies.
    \item Presented findings to stakeholders, resulting in data-driven decisions that improved product offerings.
\end{itemize}

\textbf{Data Analyst} \\
Analytics Co., Anytown, CA \\
June 2017 - August 2017 \\
\begin{itemize}[left=0pt]
    \item Analyzed large datasets to identify trends and insights for client reports.
    \item Created visualizations in Tableau that helped stakeholders understand complex data relationships.
\end{itemize}

\section*{Skills}
\begin{itemize}[left=0pt]
    \item \textbf{Technical Skills:} Python, R, SQL, IDL
    \item \textbf{Soft Skills:} Communication, Teamwork, Problem-Solving
    \item \textbf{Languages:} English (Fluent), Spanish (Conversational)
\end{itemize}

\section*{Projects}
\textbf{Customer Segmentation Analysis} \\
Conducted an analysis to segment customers based on purchasing behavior using clustering techniques, leading to targeted marketing efforts that improved customer engagement.

\section*{Certifications}
\begin{itemize}[left=0pt]
    \item Certified Data Scientist, Data Science Council of America, June 2020
    \item AWS Certified Solutions Architect, Amazon Web Services, August 2021
\end{itemize}

\section*{References}
Available upon request.

\end{document}